Perihelion advance of Mercury

### 2019-07-07 perihelion_advance_of_mercury.Rmd
slight clarification

With all these we can simulate the orbit:
```{r}
 out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e15,len=5e5))
 plot(out$x,out$y,type='l',asp=1,axes=FALSE,xlab='',ylab='',main='Orbit of Mercury')
 event_horizon()
 max(out$phi/(2*pi))
```

>>>>

With all these we can simulate the orbit:
```{r}
 out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e15,len=5e5))
 plot(out$x,out$y,type='l',asp=1,axes=FALSE,xlab='',ylab='',main='Orbit of Mercury, Sun not to scale')
 points(0,0,pch=21,bg='yellow',col='orange') # Schwarzschild radius invisible at this scale
 max(out$phi/(2*pi))
```
